Syntactic realization with data-driven neural tree grammars

### 2016-10-11 paper/draft.tex

Figure~\ref{table:linresults} shows the NLG evaluation results for the
different models.
%
All differences in model are significant using an
Independent\footnote{An Independent t-test was used instead of a
  Paired-Sample t-test because of intermittent failures during
  linearization that resulted in slightly different numbers of
  observations.} t-test ($p<10^{-5}$).
%
For both models, the differences between structural embeddings (using convolutional coding) and atomic embeddings (using standard vector embedding techniques) were not significant, while the differences between the two embeddings and minimal embeddings were significant ($p<10^{-5}$). 
%
The performance confirms our expectation that differences in supertag
accuracy after decoding correlate with NLG accuracy overall, but that
differences in NLG performance are attenuated.
%
We note by comparison that Bangalore and Rambow report an accuracy of
74.9\% in their best evaluation of FERGUS---on a data set of just 100
sentences with an average length of 16.7.
%
Our evaluation, on 2400 sentences with an average length of 22, is
more strenuous.

>>>>

Figure~\ref{table:linresults} shows the NLG evaluation results for the
different models.
%
All differences in model are significant using an Independent t-test ($p<10^{-5}$).  \footnote{An Indepedent t-test was used instead of a Paired-Sample t-test because of intermittent failures during linearization that resulted in slightly different numbers of observations.}
%
For both models, the differences between structural embeddings (using convolutional coding) and atomic embeddings (using standard vector embedding techniques) were not significant, while the differences between the two embeddings and minimal embeddings were significant ($p<10^{-5}$). 
%
The performance confirms our expectation that differences in supertag
accuracy after decoding correlate with NLG accuracy overall, but that
differences in NLG performance are attenuated.
%
We note by comparison that Bangalore and Rambow report an accuracy of
74.9\% in their best evaluation of FERGUS---on a data set of just 100
sentences with an average length of 16.7.
%
Our evaluation, on 2400 sentences with an average length of 22.1, is
more strenuous.
